---
title: "Seed influence"
author: "Suharkov MP"
date: "24 12 2020"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, warning=F, message=F, echo=F}
# Load all required packages (list was taken from https://www.mzes.uni-mannheim.de/socialsciencedatalab/article/advancing-text-mining/)
library(tidyverse)        # Also loads dplyr, ggplot2, and haven
library(quanteda)         # For NLP
#library(readtext)        # To read .txt files
library(stringi)          # corpus analysis
library(stm)              # For structural topic models
library(stminsights)      # For visual exploration of STM
library(wordcloud)        # To generate wordclouds
library(gsl)              # Required for the topicmodels package
library(topicmodels)      # For topicmodels
library(caret)            # For machine learning
library(tm)               #text analisys
```

# Overview

This paper is my attempt to find if there any influence of chosen seed at the word distribution. As before, the en_US locale is used. 

Load the whole data:
```{r data, warning=F, message=F, echo=F}
blogs <- corpus(readLines('./final/en_US/en_US.blogs.txt'))
news <- corpus(readLines('./final/en_US/en_US.news.txt'))
twitter <- corpus(readLines('./final/en_US/en_US.twitter.txt'))
```

Now seeds, I used a method of typing random numbers by keyboard, so they are true-random, not pseudo.
## Seed 362
```{r seed362, warning=F, message=F}
set.seed(362)
blogs362 <- corpus_sample(blogs, size = 5000)
news362 <- corpus_sample(news, size = 5000)
twitter362 <- corpus_sample(twitter, size = 5000)
docnames(blogs362) <- c(1:5000)
docnames(news362) <- c(5001:10000)
docnames(twitter362) <- c(10001:15000)
corp362 <- blogs362 + news362 + twitter362
tokens362 <- tokens(corp362)
#remove numbers and punctuation
tokens362 <- tokens(tokens362, remove_punct = T, remove_numbers = T)
#remove stopwords
tokens362 <- tokens_select(tokens362, pattern = stopwords('en'), selection = 'remove')
#remove messy symbols
```
```
## Seed 24734
```{r seed24734, warning=F, message=F}
set.seed(24734)
blogs24734 <- corpus_sample(blogs, size = 5000)
news24734 <- corpus_sample(news, size = 5000)
twitter24734 <- corpus_sample(twitter, size = 5000)
docnames(blogs24734) <- c(1:5000)
docnames(news24734) <- c(5001:10000)
docnames(twitter24734) <- c(10001:15000)
corp24734 <- blogs24734 + news24734 + twitter24734
```
## Seed 346
```{r seed346, warning=F, message=F}
set.seed(346)
blogs346 <- corpus_sample(blogs, size = 5000)
news346 <- corpus_sample(news, size = 5000)
twitter346 <- corpus_sample(twitter, size = 5000)
docnames(blogs346) <- c(1:5000)
docnames(news346) <- c(5001:10000)
docnames(twitter346) <- c(10001:15000)
corp346 <- blogs346 + news346 + twitter346
```
## Seed 12354
```{r seed12354, warning=F, message=F}
set.seed(12354)
blogs12354 <- corpus_sample(blogs, size = 5000)
news12354 <- corpus_sample(news, size = 5000)
twitter12354 <- corpus_sample(twitter, size = 5000)
docnames(blogs12354) <- c(1:5000)
docnames(news12354) <- c(5001:10000)
docnames(twitter12354) <- c(10001:15000)
corp12354 <- blogs12354 + news12354 + twitter12354
```
## Seed 47
```{r seed47, warning=F, message=F}
set.seed(47)
blogs47 <- corpus_sample(blogs, size = 5000)
news47 <- corpus_sample(news, size = 5000)
twitter47 <- corpus_sample(twitter, size = 5000)
docnames(blogs47) <- c(1:5000)
docnames(news47) <- c(5001:10000)
docnames(twitter47) <- c(10001:15000)
corp47 <- blogs47 + news47 + twitter47
```
## Seed 4754
```{r seed4754, warning=F, message=F}
set.seed(4754)
blogs4754 <- corpus_sample(blogs, size = 5000)
news4754 <- corpus_sample(news, size = 5000)
twitter4754 <- corpus_sample(twitter, size = 5000)
docnames(blogs4754) <- c(1:5000)
docnames(news4754) <- c(5001:10000)
docnames(twitter4754) <- c(10001:15000)
corp4754 <- blogs4754 + news4754 + twitter4754
```
## Seed 234
```{r seed234, warning=F, message=F}
set.seed(234)
blogs234 <- corpus_sample(blogs, size = 5000)
news234 <- corpus_sample(news, size = 5000)
twitter234 <- corpus_sample(twitter, size = 5000)
docnames(blogs234) <- c(1:5000)
docnames(news234) <- c(5001:10000)
docnames(twitter234) <- c(10001:15000)
corp234 <- blogs234 + news234 + twitter234
```
## Seed 67
```{r seed67, warning=F, message=F}
set.seed(67)
blogs67 <- corpus_sample(blogs, size = 5000)
news67 <- corpus_sample(news, size = 5000)
twitter67 <- corpus_sample(twitter, size = 5000)
docnames(blogs67) <- c(1:5000)
docnames(news67) <- c(5001:10000)
docnames(twitter67) <- c(10001:15000)
corp67 <- blogs67 + news67 + twitter67
```
## Seed 780
```{r seed780, warning=F, message=F}
set.seed(780)
blogs780 <- corpus_sample(blogs, size = 5000)
news780 <- corpus_sample(news, size = 5000)
twitter780 <- corpus_sample(twitter, size = 5000)
docnames(blogs780) <- c(1:5000)
docnames(news780) <- c(5001:10000)
docnames(twitter780) <- c(10001:15000)
corp780 <- blogs780 + news780 + twitter780
```
